Financialisation of Commodity Markets \\\large{Co-movement Behind-the-Scenes}

### 2024-12-04 docs/paper.tex
paper edits
refactor make_table function + introduce cross correlation analysis in methods section.

For each period, the weekly return series for the individual US-traded
assets are regressed on both the relative change on their respective CHP
series and that on the cross-sectional CHP independently. The resulting
\(R^{2}\) values are then averaged by sector and sub-sector.
Additionally, pairwise daily return correlations are computed for each
combination of assets across the periods of interest and for each
individual year within the full sample period. These correlation
coefficients are then averaged across the entire cross-section of
assets, as well as by country, sector, and sub-sector. For each period,
the coefficients are also calculated and averaged across phases of low
and high cross-sectional CHP.

This approach sheds light on the evolving interconnectedness among
commodity assets as the complex transitions from traditional market
dynamics---where commodity producers and speculators had distinct
roles---to a more intricate landscape shaped by the influx of financial
investors.

@@

Financialisation was a global phenomenon, through the channel of index
investment it simultaneously influenced the entire spectrum of liquid
commodities, eventually spurring the transformation of commodity markets
from a collection of idiosyncratic markets into a more cohesive
collection akin to an asset class. In this context, interconnectedness
emerges as a crucial aspect that warrants thorough examination.\\
We strive to address this issue by first examining the average returns
pairwise correlations between commodities across the entire
cross-section of the commodity assets considered in the study as well as
by country, sector and sub-sector.
Table~\ref{tbl-correlations-inner-periods} shows the results for the
four periods of interest with the results reported for the entire period
as well as for periods of \textbf{backwardation} and \textbf{contango}.
For the entire sample the average pairwise correlation jumps from 0.07
in the first period to 0.16 over financialisation. This finding
indicates higher interdependence within the full cross-section of
commodities starting with the financialisation period, consistent with
the empirical findings in \citet{fryMcKibbin_evolution_2023} and
\citet{mayer_financialization_2017} as well as with the theoretical
model of \citet{basak_model_2016}. The sector analysis sheds light on
the driving force behind these changes. The US metals see the sharpest
increase in pairwise correlations going from 0.22 over the past period
to 0.56 over financialisation while the three other sectors see a much
smaller percentage increase during financialisation relative to the past
period. These results thus suggest that the US metals sector was the
driving force behind increased average pairwise correlations during
financialisation, a new observation to the best of our knowledge. The
pattern of correlations is very similar across phases of
\textbf{backwardation} and \textbf{contango} for all the sectors and
sub-sectors over the past and financialisation periods which indicates
that increased commodity interdependence over financialisation was not a
phase driven phenomenon in the same way that individual commodity
returns are, as demonstrated in Table~\ref{tbl-stats-combined}.\\
We break down these average correlations by years in
Table~\ref{tbl-correlations-inner-years}. For the full sample of assets,
the average pairwise correlations remain in the 0.06--0.08 range from
1998 through 2003, before suddenly increasing to 0.12 from 2003 to 2004.
This suggests 2004 as a distinct break point for the onset of
financialisation, as noted in several studies
\citep{baker_financialization_2021, tang_index_2012}. We further observe
that the US metals appear to have played a major role in this as the
increase seems driven by the sector which average pairwise correlation
more than doubles (0.49 vs 0.22) over the period.

@@

\textbf{\cellcolor{gray!10}{Corn-\#2 yellow (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.37\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.51\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{29.54\%}} & \textcolor[HTML]{4285f4}{\textbf{36.15\%}} & \textcolor[HTML]{4285f4}{\textbf{21.8\%}}\\
\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.86\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{19.26\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.48\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-8.74\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23.07\%}} & \textcolor[HTML]{4285f4}{\textbf{29.14\%}} & \textcolor[HTML]{4285f4}{\textbf{31.59\%}} & \textcolor[HTML]{4285f4}{\textbf{21\%}}\\
\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.3\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{23.54\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.43\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.78\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{23\%}} & \textcolor[HTML]{4285f4}{\textbf{30.01\%}} & \textcolor[HTML]{4285f4}{\textbf{40.14\%}} & \textcolor[HTML]{4285f4}{\textbf{22.68\%}}\\
\textbf{\cellcolor{gray!10}{Oats (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.49\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{21.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.87\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{32.22\%}} & \textcolor[HTML]{4285f4}{\textbf{31.04\%}} & \textcolor[HTML]{4285f4}{\textbf{34.67\%}} & \textcolor[HTML]{4285f4}{\textbf{29.5\%}}\\
\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-5.39\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.82\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.85\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.56\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{29.02\%}} & \textcolor[HTML]{4285f4}{\textbf{33.82\%}} & \textcolor[HTML]{4285f4}{\textbf{31.43\%}} & \textcolor[HTML]{4285f4}{\textbf{31.55\%}}\\
\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.95\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{*35.38\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{11.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.17\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{35.22\%}} & \textcolor[HTML]{4285f4}{\textbf{28.1\%}} & \textcolor[HTML]{4285f4}{\textbf{37.7\%}} & \textcolor[HTML]{4285f4}{\textbf{27.5\%}}\\
\textbf{\cellcolor{gray!10}{Soybean meal (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{7.29\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{12.06\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.12\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.33\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{26.34\%}} & \textcolor[HTML]{4285f4}{\textbf{32.55\%}} & \textcolor[HTML]{4285f4}{\textbf{31.78\%}} & \textcolor[HTML]{4285f4}{\textbf{25.11\%}}\\
\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.15\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{8.22\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.52\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{27.77\%}} & \textcolor[HTML]{4285f4}{\textbf{33.06\%}} & \textcolor[HTML]{4285f4}{\textbf{25.7\%}} & \textcolor[HTML]{4285f4}{\textbf{25.1\%}}\\
\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{1.52\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.91\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.32\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{2.22\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{24.94\%}} & \textcolor[HTML]{4285f4}{\textbf{32.13\%}} & \textcolor[HTML]{4285f4}{\textbf{36.85\%}} & \textcolor[HTML]{4285f4}{\textbf{25.32\%}}\\
\textbf{\cellcolor{gray!10}{Soybean oil (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.21\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{15.57\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{4.04\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-7.39\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.43\%}} & \textcolor[HTML]{4285f4}{\textbf{28.35\%}} & \textcolor[HTML]{4285f4}{\textbf{25.75\%}} & \textcolor[HTML]{4285f4}{\textbf{18.95\%}}\\
\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.79\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{14.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{20.34\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-9.44\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.35\%}} & \textcolor[HTML]{4285f4}{\textbf{28.94\%}} & \textcolor[HTML]{4285f4}{\textbf{22.33\%}} & \textcolor[HTML]{4285f4}{\textbf{18.19\%}}\\
\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-2.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{16.62\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-10.01\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-4.12\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.55\%}} & \textcolor[HTML]{4285f4}{\textbf{27.91\%}} & \textcolor[HTML]{4285f4}{\textbf{28.65\%}} & \textcolor[HTML]{4285f4}{\textbf{19.79\%}}\\
\textbf{\cellcolor{gray!10}{Soybeans (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.89\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.36\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.19\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-3.82\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.47\%}} & \textcolor[HTML]{4285f4}{\textbf{30.04\%}} & \textcolor[HTML]{4285f4}{\textbf{28\%}} & \textcolor[HTML]{4285f4}{\textbf{21.22\%}}\\
\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{backwardation}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.69\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.93\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{13.42\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-11.45\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.93\%}} & \textcolor[HTML]{4285f4}{\textbf{34.58\%}} & \textcolor[HTML]{4285f4}{\textbf{24.39\%}} & \textcolor[HTML]{4285f4}{\textbf{22.04\%}}\\
\textbf{\cellcolor{gray!10}{}} & \textbf{\cellcolor{gray!10}{contango}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-0.16\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{25.71\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{0.96\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{3.75\%}}}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{\textbf{21.09\%}} & \textcolor[HTML]{4285f4}{\textbf{24.74\%}} & \textcolor[HTML]{4285f4}{\textbf{31.11\%}} & \textcolor[HTML]{4285f4}{\textbf{20.56\%}}\\
\textbf{\cellcolor{gray!10}{Wheat-SRW (XCBT)}} & \textbf{\cellcolor{gray!10}{whole period}} & \textbf{\cellcolor{gray!10}{mean}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{5.07\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{17.63\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{6.68\%}}} & \textcolor[HTML]{4285f4}{\textbf{\cellcolor{gray!10}{-1.58\%}}}\\

>>>>

For each period, the weekly return series for the individual US-traded
assets are regressed on both the relative change on their respective CHP
series and that on the cross-sectional CHP independently. The resulting
\(R^{2}\) values are then averaged by sector and sub-sector.
Additionally, pairwise daily return correlations are computed for each
combination of assets across the periods of interest and for each
individual year within the full sample period. These correlation
coefficients are then averaged across the entire cross-section of
assets, as well as by country, sector, and sub-sector. For each period,
the coefficients are also calculated and averaged independently over
phases of low and high cross-sectional CHP. We further form equally
weighted portfolios by country, by grouping together the US and GB
traded assets independently, as well a by sector and sub-sector for the
US traded assets. For each period we compute the correlation coefficient
between the two country portfolios as well as the average pairwise
correlation coefficients between the sector and sub-sector portfolios;
these are computed over the entire period as well as over phases of low
and high cross-sectional CHP.\\
This approach sheds light on the evolving interconnectedness among
commodity assets as the complex transitions from traditional market
dynamics---where commodity producers and speculators had distinct
roles---to a more intricate landscape shaped by the influx of financial
investors.

@@

Financialisation was a global phenomenon, through the channel of index
investment it simultaneously influenced the entire spectrum of liquid
commodities, eventually spurring the transformation of commodity markets
from a collection of idiosyncratic markets into a more cohesive
collection akin to an asset class. In this context, interconnectedness
emerges as a crucial aspect that warrants thorough examination.\\
We strive to address this issue by first examining the average returns
pairwise correlations between commodities across the entire
cross-section of the commodity assets considered in the study as well as
by country, sector and sub-sector.
Table~\ref{tbl-correlations-inner-periods} shows the results for the
four periods of interest with the results reported for the entire period
as well as for periods of \textbf{backwardation} and \textbf{contango}.
For the entire sample the average pairwise correlation jumps from 0.07
in the first period to 0.16 over financialisation. This finding
indicates higher interdependence within the full cross-section of
commodities starting with the financialisation period, consistent with
the empirical findings in \citet{fryMcKibbin_evolution_2023} and
\citet{mayer_financialization_2017} as well as with the theoretical
model of \citet{basak_model_2016}. The sector analysis sheds light on
the driving force behind these changes. The US metals see the sharpest
increase in pairwise correlations going from 0.22 over the past period
to 0.56 over financialisation while the three other sectors see a much
smaller percentage increase during financialisation relative to the past
period. These results thus suggest that the US metals sector was the
driving force behind increased average pairwise correlations during
financialisation, a new observation to the best of our knowledge. The
pattern of correlations is very similar across phases of
\textbf{backwardation} and \textbf{contango} for all the sectors and
sub-sectors over the past and financialisation periods which indicates
that increased commodity interdependence over financialisation was not a
phase driven phenomenon in the same way that individual commodity
returns are, as demonstrated in Table~\ref{tbl-stats-combined}.\\
We break down these average correlations by year in
Table~\ref{tbl-correlations-inner-years}. For the full sample of assets,
the average pairwise correlations remain in the 0.06--0.08 range from
1998 through 2003, before suddenly increasing to 0.12 from 2003 to 2004.
This suggests 2004 as a distinct break point for the onset of
financialisation, as noted in several studies
\citep{baker_financialization_2021, tang_index_2012}. We further observe
that the US metals appear to have played a major role in this as the
increase seems driven by the sector which average pairwise correlation
more than doubles (0.49 vs 0.22) over the period.

@@

\textbf{Corn-\#2 yellow (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.48\%} & \textcolor[HTML]{4285f4}{21.37\%} & \textcolor[HTML]{4285f4}{6.89\%} & \textcolor[HTML]{4285f4}{-4.51\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23\%} & \textcolor[HTML]{4285f4}{29.54\%} & \textcolor[HTML]{4285f4}{36.15\%} & \textcolor[HTML]{4285f4}{21.8\%}\\
\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-4.86\%} & \textcolor[HTML]{4285f4}{19.26\%} & \textcolor[HTML]{4285f4}{20.48\%} & \textcolor[HTML]{4285f4}{-8.74\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23.07\%} & \textcolor[HTML]{4285f4}{29.14\%} & \textcolor[HTML]{4285f4}{31.59\%} & \textcolor[HTML]{4285f4}{21\%}\\
\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.3\%} & \textcolor[HTML]{4285f4}{23.54\%} & \textcolor[HTML]{4285f4}{-4.43\%} & \textcolor[HTML]{4285f4}{0.78\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{23\%} & \textcolor[HTML]{4285f4}{30.01\%} & \textcolor[HTML]{4285f4}{40.14\%} & \textcolor[HTML]{4285f4}{22.68\%}\\
\textbf{Oats (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.49\%} & \textcolor[HTML]{4285f4}{21.62\%} & \textcolor[HTML]{4285f4}{8.89\%} & \textcolor[HTML]{4285f4}{-0.87\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{32.22\%} & \textcolor[HTML]{4285f4}{31.04\%} & \textcolor[HTML]{4285f4}{34.67\%} & \textcolor[HTML]{4285f4}{29.5\%}\\
\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-5.39\%} & \textcolor[HTML]{4285f4}{7.82\%} & \textcolor[HTML]{4285f4}{7.85\%} & \textcolor[HTML]{4285f4}{2.56\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{29.02\%} & \textcolor[HTML]{4285f4}{33.82\%} & \textcolor[HTML]{4285f4}{31.43\%} & \textcolor[HTML]{4285f4}{31.55\%}\\
\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{16.95\%} & \textcolor[HTML]{4285f4}{*35.38\%} & \textcolor[HTML]{4285f4}{11.68\%} & \textcolor[HTML]{4285f4}{-3.17\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{35.22\%} & \textcolor[HTML]{4285f4}{28.1\%} & \textcolor[HTML]{4285f4}{37.7\%} & \textcolor[HTML]{4285f4}{27.5\%}\\
\textbf{Soybean meal (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{7.29\%} & \textcolor[HTML]{4285f4}{12.06\%} & \textcolor[HTML]{4285f4}{8.12\%} & \textcolor[HTML]{4285f4}{-0.33\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{26.34\%} & \textcolor[HTML]{4285f4}{32.55\%} & \textcolor[HTML]{4285f4}{31.78\%} & \textcolor[HTML]{4285f4}{25.11\%}\\
\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{13.15\%} & \textcolor[HTML]{4285f4}{8.22\%} & \textcolor[HTML]{4285f4}{16.04\%} & \textcolor[HTML]{4285f4}{-3.52\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{27.77\%} & \textcolor[HTML]{4285f4}{33.06\%} & \textcolor[HTML]{4285f4}{25.7\%} & \textcolor[HTML]{4285f4}{25.1\%}\\
\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{1.52\%} & \textcolor[HTML]{4285f4}{15.91\%} & \textcolor[HTML]{4285f4}{2.32\%} & \textcolor[HTML]{4285f4}{2.22\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.94\%} & \textcolor[HTML]{4285f4}{32.13\%} & \textcolor[HTML]{4285f4}{36.85\%} & \textcolor[HTML]{4285f4}{25.32\%}\\
\textbf{Soybean oil (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.21\%} & \textcolor[HTML]{4285f4}{15.57\%} & \textcolor[HTML]{4285f4}{4.04\%} & \textcolor[HTML]{4285f4}{-7.39\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.43\%} & \textcolor[HTML]{4285f4}{28.35\%} & \textcolor[HTML]{4285f4}{25.75\%} & \textcolor[HTML]{4285f4}{18.95\%}\\
\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{14.79\%} & \textcolor[HTML]{4285f4}{14.62\%} & \textcolor[HTML]{4285f4}{20.34\%} & \textcolor[HTML]{4285f4}{-9.44\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.35\%} & \textcolor[HTML]{4285f4}{28.94\%} & \textcolor[HTML]{4285f4}{22.33\%} & \textcolor[HTML]{4285f4}{18.19\%}\\
\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.68\%} & \textcolor[HTML]{4285f4}{16.62\%} & \textcolor[HTML]{4285f4}{-10.01\%} & \textcolor[HTML]{4285f4}{-4.12\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.55\%} & \textcolor[HTML]{4285f4}{27.91\%} & \textcolor[HTML]{4285f4}{28.65\%} & \textcolor[HTML]{4285f4}{19.79\%}\\
\textbf{Soybeans (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{6.89\%} & \textcolor[HTML]{4285f4}{13.36\%} & \textcolor[HTML]{4285f4}{6.19\%} & \textcolor[HTML]{4285f4}{-3.82\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.47\%} & \textcolor[HTML]{4285f4}{30.04\%} & \textcolor[HTML]{4285f4}{28\%} & \textcolor[HTML]{4285f4}{21.22\%}\\
\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{13.69\%} & \textcolor[HTML]{4285f4}{0.93\%} & \textcolor[HTML]{4285f4}{13.42\%} & \textcolor[HTML]{4285f4}{-11.45\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.93\%} & \textcolor[HTML]{4285f4}{34.58\%} & \textcolor[HTML]{4285f4}{24.39\%} & \textcolor[HTML]{4285f4}{22.04\%}\\
\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.16\%} & \textcolor[HTML]{4285f4}{25.71\%} & \textcolor[HTML]{4285f4}{0.96\%} & \textcolor[HTML]{4285f4}{3.75\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{21.09\%} & \textcolor[HTML]{4285f4}{24.74\%} & \textcolor[HTML]{4285f4}{31.11\%} & \textcolor[HTML]{4285f4}{20.56\%}\\
\textbf{Wheat-SRW (XCBT)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{5.07\%} & \textcolor[HTML]{4285f4}{17.63\%} & \textcolor[HTML]{4285f4}{6.68\%} & \textcolor[HTML]{4285f4}{-1.58\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.93\%} & \textcolor[HTML]{4285f4}{33.03\%} & \textcolor[HTML]{4285f4}{37.62\%} & \textcolor[HTML]{4285f4}{26.58\%}\\
\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{-2.7\%} & \textcolor[HTML]{4285f4}{19.02\%} & \textcolor[HTML]{4285f4}{0.98\%} & \textcolor[HTML]{4285f4}{0.44\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{25.79\%} & \textcolor[HTML]{4285f4}{36\%} & \textcolor[HTML]{4285f4}{37.53\%} & \textcolor[HTML]{4285f4}{26.57\%}\\
\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{11.78\%} & \textcolor[HTML]{4285f4}{16.29\%} & \textcolor[HTML]{4285f4}{14.57\%} & \textcolor[HTML]{4285f4}{-2.77\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{24.04\%} & \textcolor[HTML]{4285f4}{29.84\%} & \textcolor[HTML]{4285f4}{37.73\%} & \textcolor[HTML]{4285f4}{26.72\%}\\
\textbf{Cattle-feeder (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.39\%} & \textcolor[HTML]{4285f4}{7.43\%} & \textcolor[HTML]{4285f4}{7.13\%} & \textcolor[HTML]{4285f4}{1.87\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.23\%} & \textcolor[HTML]{4285f4}{15.16\%} & \textcolor[HTML]{4285f4}{15.24\%} & \textcolor[HTML]{4285f4}{18.69\%}\\
\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{2.31\%} & \textcolor[HTML]{4285f4}{**20.52\%} & \textcolor[HTML]{4285f4}{7.51\%} & \textcolor[HTML]{4285f4}{6.58\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{12.79\%} & \textcolor[HTML]{4285f4}{14.93\%} & \textcolor[HTML]{4285f4}{13.39\%} & \textcolor[HTML]{4285f4}{20.14\%}\\
\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.81\%} & \textcolor[HTML]{4285f4}{-5.49\%} & \textcolor[HTML]{4285f4}{7.28\%} & \textcolor[HTML]{4285f4}{-3.12\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{13.67\%} & \textcolor[HTML]{4285f4}{15.35\%} & \textcolor[HTML]{4285f4}{16.91\%} & \textcolor[HTML]{4285f4}{17.23\%}\\
\textbf{Cattle-live (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{3.45\%} & \textcolor[HTML]{4285f4}{8.77\%} & \textcolor[HTML]{4285f4}{4.13\%} & \textcolor[HTML]{4285f4}{1.92\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.1\%} & \textcolor[HTML]{4285f4}{17.43\%} & \textcolor[HTML]{4285f4}{16.32\%} & \textcolor[HTML]{4285f4}{18.3\%}\\
\textbf{} & \textbf{backwardation} & \textbf{mean} & \textcolor[HTML]{4285f4}{8.39\%} & \textcolor[HTML]{4285f4}{14.2\%} & \textcolor[HTML]{4285f4}{5.87\%} & \textcolor[HTML]{4285f4}{-2.07\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{16.65\%} & \textcolor[HTML]{4285f4}{17.91\%} & \textcolor[HTML]{4285f4}{14.97\%} & \textcolor[HTML]{4285f4}{19.9\%}\\
\textbf{} & \textbf{contango} & \textbf{mean} & \textcolor[HTML]{4285f4}{-0.34\%} & \textcolor[HTML]{4285f4}{3.43\%} & \textcolor[HTML]{4285f4}{2.7\%} & \textcolor[HTML]{4285f4}{5.82\%}\\
\textbf{} & \textbf{} & \textbf{volatility} & \textcolor[HTML]{4285f4}{17.49\%} & \textcolor[HTML]{4285f4}{16.99\%} & \textcolor[HTML]{4285f4}{17.57\%} & \textcolor[HTML]{4285f4}{16.66\%}\\
\textbf{Lean hogs (XCME)} & \textbf{whole period} & \textbf{mean} & \textcolor[HTML]{4285f4}{0.73\%} & \textcolor[HTML]{4285f4}{8.4\%} & \textcolor[HTML]{4285f4}{12.69\%} & \textcolor[HTML]{4285f4}{-1.09\%}\\
